---
title: "metaRbolomics dependencies"
author: "Steffen Neumann"
date: "August 26, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("repos" = list(CRAN="http://cran.rstudio.com/"))

library(miniCRAN)
source("miniMetabolomicsHelper.R")

```


```{r packages}

url="http://www.bioconductor.org/packages/3.9/bioc/"

all_pkgs <- biocAndCranPackages(bioc_url=url)
views <- c("Metabolomics", "Cheminformatics", "Lipidomics", "SystemsBiology")

packagesAndViews <- allPackagesInViews(url)

vpkgs <- lapply(views, function(view) packagesInView(view, packagesAndViews=packagesAndViews))
names(vpkgs) <- views
```

The Comprehensive R Archive Network (better known as CRAN) repository contains more than `r table(all_pkgs)["http://cran.rstudio.com/src/contrib"]` packages for many application areas.


| Repository                 | No. of packages                       |
| -------------------------- | -------------------------------------:|
| CRAN                       | `r table(all_pkgs)["http://cran.rstudio.com/src/contrib"]`   |
| BioC                       | `r table(all_pkgs[,"Repository"])[paste(url, "src/contrib", sep="")]`   |


On BioC, packages are sorted (by their respective authors) into “BioC Views”, where the most relevant ones for metabolomics are Cheminformatics (`r length(vpkgs[["Cheminformatics"]])`), Lipidomics (`r length(vpkgs[["Lipidomics"]])`), SystemsBiology (`r length(vpkgs[["SystemsBiology"]])`) and, of course, Metabolomics (`r length(vpkgs[["Metabolomics"]])`).



| View                 | No. of packages                       |
| -------------------- | -------------------------------------:|
| Metabolomics         | `r length(vpkgs[["Metabolomics"]])`   |
| Cheminformatics      | `r length(vpkgs[["Cheminformatics"]])`|
| Lipidomics           | `r length(vpkgs[["Lipidomics"]])`     |
| SystemsBiology       | `r length(vpkgs[["SystemsBiology"]])` |

## SessionInfo

This page was created with the following packages:

```{r sessionInfo}
sessionInfo()
```
